### 2024-10-07 esop25/cpj.tex
checkpoint

\subsubsection{Type Safety}

@@

    \eqj{R_1}{\eqs}{\toeq{\elab{\be}{\cid}}}{\ty_0}
  \end{mathpar}
  are both valid, and by the induction hypothesis $\Gamma_0$ is sound for $\prog_0$.     
\end{proof}

Our main type safety result combines typing and leakage judgements,
and guarantees gradual release of protocols-- that is, that adversarial
messages reflect no dependencies on honest secrets.
\cnote{Need to define gradual release... should probably have a section
  where we summarize hyperproperties.}
\begin{theorem}
  Given $\prog$ with $\views(\prog) = M \cup P$, if $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$
  is valid and for all $H,C$ we have $\leakj{\Gamma}{M_C}{T}$ with $T$ closed
  and $S_H \cap T = \varnothing$, then $\prog$ satisfies gradual release.
\end{theorem}
\begin{proof}
  Immediate by Lemma \ref{lemma-cpjsound}. \qed
\end{proof}

>>>>

\subsubsection{Type Soundness}

@@

    \eqj{R_1}{\eqs}{\toeq{\elab{\be}{\cid}}}{\ty_0}
  \end{mathpar}
  are both valid, and by the induction hypothesis $\Gamma_0$ is sound for $\prog_0$.
  We can then proceed by a second induction on the derivation of $\ty_0$, where there
  are two subcases. XXX
\end{proof}

Our main type soundness result combines typing and leakage judgements,
and guarantees gradual release of protocols-- that is, that adversarial
messages reflect no dependencies on honest secrets.
\cnote{Need to define gradual release... should probably have a section
  where we summarize hyperproperties.}
\begin{theorem}
  Given $\prog$ with $\views(\prog) = M \cup P$, if $\cpj{R}{\eqs}{\eqspre \wedge \toeq{\prog}}{\Gamma}$
  is valid and for all $H,C$ we have $\leakj{\Gamma}{M_C}{T}$ with $T$ closed
  and $S_H \cap T = \varnothing$, then $\prog$ satisfies gradual release.
\end{theorem}
\begin{proof}
  Immediate by Lemma \ref{lemma-cpjsound}. \qed
\end{proof}

### 2024-10-07 esop25/ipj.tex
checkpoint

\subsubsection{Type Safety}

\begin{definition}
  Given $H,C$ and $\prog$ with $\views(\prog) = V$ and $\secrets(\prog) = S$,
  $\adversary$, and $\store \in \aruns(\prog)$, we say $\store$ is
  \emph{abberant} if $\neg\exists \store' \in \runs(\prog) .
  \store_{S_H \cup V} = \store'_{S_H \cup V}$, in which case we say
  any $x \in V$ \emph{has an abberation}.
\end{definition}

@@

Our main type safety result for integrity is then given as follows.
\begin{theorem}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$ with
  $\views(\prog) = V$, if
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and for all $H,C$ with $\cheatj{\Delta}{H,C}{\seclev}$ 
  we have $\seclev(x) = \hilab$ for all $x \in \houtputs$, then $\prog$
  has integrity.
\end{theorem}

>>>>

\subsubsection{Type Soundness}

\begin{definition}
  Given $H,C$ and $\prog$ with $\views(\prog) = V$ and $\secrets(\prog) = S$,
  $\adversary$, and $\store \in \aruns(\prog)$, we say $\store$ is
  \emph{abberant} if $\neg\exists \store' \in \runs(\prog) .
  \store_{S_H \cup V} = \store'_{S_H \cup V}$, and if
   $\neg\exists \store' \in \runs(\prog) .
  \store_{S_H \cup \{ x \}} = \store'_{S_H \cup \{ x \}}$ we say
  any $x \in V$ \emph{has an abberation}.
\end{definition}

@@

Our main type soundness result for integrity is then given as follows.
\begin{theorem}
  Given pre-processing predicate $\eqspre$ and protocol $\prog$ with
  $\views(\prog) = V$, if
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and for all $H,C$ with $\cheatj{\Delta}{H,C}{\seclev}$ 
  we have $\seclev(x) = \hilab$ for all $x \in \houtputs$, then $\prog$
  has integrity for all $H,C$.
\end{theorem}
